Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-25 paper/snakemajoranas.tex
edit band structure caption

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Figure of the band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
The blue lines correspond to $\phi=0$, $B=0$ (trivial phase) and the orange lines to $\phi=\pi$, $B = \SI{1}{T}$ (topological phase).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
On the $x$-axis is the folded lattice momentum where $z_x=\SI{1300}{\nm}$.
Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=\frac{dE}{dk}$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes most insensitive to the momentum $k_x$, and thus the $v_\textrm{F}$ decreases.
As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
The parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
% TODO: mention z_x!
\end{figure}

>>>>

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Band stuctures corresponding to the system in Fig.~\ref{fig:setup} with different zigzag amplitudes.
The blue lines correspond to $\phi=0$, $B=0$ (trivial phase) and the orange lines to $\phi=\pi$, $B = \SI{1}{T}$ (topological phase).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=\frac{W}{2}$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
On the $x$-axis is the folded lattice momentum where $z_x=\SI{1300}{\nm}$.
Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=\frac{dE}{dk}$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
As the zigzag amplitude increases the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana decay length because $\xi_M \propto \frac{v_\textrm{F}}{E_\textrm{gap}}$
The parameters values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
\end{figure}
